A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$ methods

### 2025-03-05 paper_v02/article.tex
tests

>>>>

The algorithm was tested with data and results from the \citep{RIBEIRO2025107419}, the original data came from the \textit{Physionet} open-access website, available at this link:

\begin{center}
	\url{https://physionet.org/content/eegmmidb/1.0.0/}
\end{center} 
This comprehensive dataset, with 108 subjects processes for all the 12 experiments, with the $\rho_{DCCA}$ and $DMC_{x}^{2}$ calculated for all the subjects and experiments, where used to compare result and validate the implementations.

Regarding performance, the pure \proglang{Python} implementation, the \proglang{Zig} implementation and the optimized \proglang{Zig} where compared with 3 oder packages that calculates the $\rho_{DCCA}$. Researching the \proglang{R} \textbf{CRAN} package repository, the \pkg{DCCA} \pkg{DFA} packages where found, and, from the \proglang{Python} \textbf{pypi}, the \pkg{DCCA} package was used.

The \pkg{DFA} is a pure \proglang{R} implementation. The \pkg{DCCA} is a \proglang{R} package with a \proglang{Java} implementation. The \pkg{DCCA} is a \proglang{Python} implementation with massive use of \pkg{Numpy} broadcasting capabilities and memory access with strides to avoid loops.

Regarding performance
